---
---
title: "JANET_RGBIF"
author: "James Lee"
date: "18/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
#relevant libraries
library(rgbif)
library(openssl)
library(spocc)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(plotly)
library(ggspatial)
library(rnaturalearth)
library(tidygeocoder)
library(ggrepel)
library(sf)
library(rgeos)
```

##List of Species

A testing data set. Below we read in the data.

```{r}
List_of_Species = read.csv('D:/Janet.csv')
head(List_of_Species)
```

##Using the gbif API

We can access the gbif API to give us relevant information about each species whilst also simultaneously using this information to clean our results. (I separately mutate multiple columns within each dataframe retrieved from the API to show the information we use to plot later)

```{r}
X = List_of_Species %>%
  mutate(keys = map(Taxon, function(x) name_backbone(name = x)$speciesKey)) %>% # obtain initial dataframe information by using keys 
  mutate(rgbif_pull  = map(keys, occ_search, limit = 200)) %>% # use keys to gather dataframe information
  mutate(Latitude = map(rgbif_pull, pluck, 'data', 'decimalLatitude')) %>% #pluck latitude
  mutate(Longitude = map(rgbif_pull, pluck, 'data', 'decimalLongitude')) %>%# pluck longitude
  mutate(Year = map(rgbif_pull, pluck, 'data', 'year')) %>% # pluck year
  mutate(Source = map(rgbif_pull, pluck, 'data', 'datasetName')) %>% # pluck source
  select(Taxon, Latitude, Longitude, Year, Source) %>% # obtain latitude and longitude occurrence data
  filter(Longitude != 'NULL') %>% # filter NULLs
  filter(Source != 'NULL') %>%
  filter(Year != 'NULL')

P = c()

#for loop to clean data and get it into a format we care about and we can easily plot

for (i in 1:nrow(X)) {
  Y = cbind(X$Latitude[[i]],X$Longitude[[i]])
  Z = cbind(X$Year[[i]],X$Source[[i]])
  O = rep(X$Taxon[i], each = nrow(Y))
  Q = cbind(O,Y,Z)
  P = rbind(P,Q)
}

#produce a tibble with renamed headers and make Species a factor

ALL_DATA = P %>%
  as_tibble %>%
  na.omit() %>%
  rename(., c(Species = O, Lat = V2, Lon = V3, Year = V4, Source = V5)) %>%
  mutate(Lat = as.double(Lat)) %>%
  mutate(Lon = as.double(Lon)) %>%
  mutate(Species = as.factor(Species)) %>%
  filter(Lon < 98, Lon > 68, Lat < 37, Lat > 8)

head(ALL_DATA)
```

Now we have a dataframe which contains co-ordinate data for all the species we care about and the relevant year and source of occurrence 

```{r message=FALSE, warning=FALSE}
world = ne_countries(country = 'india') %>%
  st_as_sf()

test_plot = ggplot() +
  geom_sf(data = world) +
  geom_point(data = ALL_DATA, 
             aes(x = Lon, y = Lat, fill = Species, color = Year, label = Source),
             size = 0.5) +
  theme(legend.position = 'none')
  

ggplotly(test_plot)
```

